\Large \bf 3-Step, 1-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-06 paper.tex
Results/Imposter attack

\subsection*{Abstract}
In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all subjects, we achieve a best-case XX\% false acceptance, XX\% false rejection rate with data from only one earpiece. In a preliminary test of an ``imposter'' spoof attack, we find a 0\% false acceptance rate. \underline{Conclusions and relevance}.

@@

\subsection{{\bfseries\sffamily TODO} Imposter attack}
\label{sec:orgac58a1b}

@@

\item Counter to expectations: referencing same side appears to be an improvement vs. across the head; use of conductive gel resulting in ability to achieve good impedances on others’ earpieces; FP1 not performing as well as expected.
\end{enumerate}

>>>>

\subsection*{Abstract}
In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all subjects, we achieve a best-case XX\% false acceptance, XX\% false rejection rate with data from only one earpiece. In a preliminary test of an ``imposter'' spoofing attack, we find a 0\% false acceptance rate. \underline{Conclusions and relevance}.

@@

\subsection{Imposter attack}

While our left-ear results establish that passthoughts achieve low FAR and FRR when tested against other subjects' passthoughts, we do not know how robust passthoughts are against a spoofing attack, in which both a subject's custom-fit electrode, and details of that subject's chosen passthought, are leaked.

To explore this scenario, we chose one subject (subject 6), and referred to their report of chosen passsthoughts. We recorded spoofed passthoughts for two ``imposter'' subjects. One subject appeared in our initial pool performing their own passthoughts (subject 2), while the other subject did not appear in the initial pool, and thus was not included when training subject classifiers. (How well the imposters were able to spoof subject 6's passthought is an open question; see Discussion).

For each task, we ran the spoofed version of the task through the classifier trained on subject 6's task as the passthought.
None of the spoofed passthoughts were accepted, resulting in a 0\% FAR.

@@

\item Counter to expectations: referencing same side appears to be an improvement vs. across the head; use of conductive gel resulting in ability to achieve good impedances on others’ earpieces; FP1 not performing as well as expected.

\item Really saw inherence factor at work in imposter attack. What part of the song? How do you imagine the face? etc
\end{enumerate}
